Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-08-13 paperIEEE.tex
Minor edits.
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@147 db7c848b-7755-4df2-b763-8796797afa52

%% Author and Affiliation (multiple authors with multiple affiliations)
\author{Stefan~Eilemann\thanks{email: eilemann@gmail.com},
        David~Steiner\thanks{email: steiner@ifi.uzh.ch} \\ %
        and~Renato~Pajarola\thanks{email:pajarola@acm.org},~\IEEEmembership{Senior Member,~IEEE}%
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem All authors are with the
Visualization and MultiMedia Lab, Department of Informatics, University of
Z\"urich.}}

%\author{Stefan Eilemann\thanks{email: eilemann@gmail.com} \\ %
%\and Renato Pajarola~\IEEEmembership{Senior Member,~IEEE}\thanks{email:
%pajarola@acm.org}}

@@

Cross-segment load balancing (CSLB, \fig{fig:vieweq}) optimizes resource
allocation of $n$ rendering resources to $m$ output channels (with $n\geq m$).
A view equalizer works in conjunction with load equalizers balancing the
individual output channels. It monitors the usage of shared source channels
across outputs and activates them to balance the rendering time of all outputs.
CSLB is unique in that it supports load balancing for planar and non-planar
visualization systems, as well as a flexible allocation of rendering resources
to individual output channels. In \cite{EEP:11}, we provide a detailed
description and evaluation of our algorithm and show that it significantly
improve performance over a static allocation.

@@

For sort-first and sort-last rendering we present static and load-balanced task
decomposition. For readability, we only present the results of the equalizer
(load or tree) providing the better performance for each application.
Unsurprisingly, static decompositions perform worse over load-balanced
compounds. Sort-first polygon rendering exhibits oscillations in performance as
nodes are added to the task, due to unfavorable assignment of a tile with a
high work load on odd node counts. Static sort-last volume rendering has a
similar oscillation behaviour, as ranges of scene geometry tend to also get
unfavorably assigned under such conditions. For our polygonal rendering setup,
the amount of data exceeds the GPU memory, therefore sort-last rendering
exhibits a better scaling behaviour since it reduces the amount of geometry
data per GPU. For volume rendering, sort-first performs better since it has
less compositing overhead and is easy to load balance.

@@

During data synchronization, the master commits the object data to all mapped
slave instances simultaneously. This is a ``push'' operation, whereas the
mapping is a slave-triggered ``pull'' operation. During commit, the buffers
only have to be serialized and compressed once, and then can be sent directly
to all mapped slave nodes. Slave nodes queue this data and consume it during
synchronization. In contrast, object mapping needs to wait for each slave node
to request the mapping, and then may need to reserialize and compress the
object data. We test the time to commit and sync the data using different
compression engines.

>>>>

%% Author and Affiliation (multiple authors with multiple affiliations)
\author{Stefan~Eilemann\thanks{email: eilemann@gmail.com},
        David~Steiner\thanks{email: steiner@ifi.uzh.ch} \\ %
        and~Renato~Pajarola\thanks{email: pajarola@ifi.uzh.ch},~\IEEEmembership{Senior Member,~IEEE}%
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem All authors are with the
Visualization and MultiMedia Lab, Department of Informatics, University of
Z\"urich.}}

%\author{Stefan Eilemann\thanks{email: eilemann@gmail.com} \\ %
%\and Renato Pajarola~\IEEEmembership{Senior Member,~IEEE}\thanks{email:
%pajarola@ifi.uzh.ch}}

@@

Cross-segment load balancing (CSLB, \fig{fig:vieweq}) optimizes resource
allocation of $n$ rendering resources to $m$ output channels (with $n\geq m$).
A view equalizer works in conjunction with load equalizers balancing the
individual output channels. It monitors the usage of shared source channels
across outputs and activates them to balance the rendering time of all outputs.
CSLB is unique in that it supports load balancing for planar and non-planar
visualization systems, as well as a flexible allocation of rendering resources
to individual output channels. In \cite{EEP:11}, we provide a detailed
description and evaluation of our algorithm and show that it significantly
improves performance over a static allocation.

@@

For sort-first and sort-last rendering we present static and load-balanced task
decomposition. For readability, we only present the results of the equalizer
(load or tree) providing the better performance for each application.
Unsurprisingly, static decompositions perform worse over load-balanced
compounds. Sort-first polygon rendering exhibits oscillations in performance as
nodes are added to the task, due to unfavorable assignment of a tile with a
high work load on odd node counts. Static sort-last volume rendering has a
similar oscillation behaviour, as ranges of scene geometry tend to also get
unfavorably assigned under such conditions. For our polygonal rendering setup,
the amount of data exceeds the GPU memory, therefore, sort-last rendering
exhibits a better scaling behaviour since it reduces the amount of geometry
data per GPU. For volume rendering, sort-first performs better since it has
less compositing overhead and is easy to load balance.

@@

During data synchronization, the master commits the object data to all mapped
slave instances simultaneously. This is a ``push'' operation, whereas the
mapping is a slave-triggered ``pull'' operation. During commit, the buffers
only have to be serialized and compressed once, and can then be sent directly
to all mapped slave nodes. Slave nodes queue this data and consume it during
synchronization. In contrast, object mapping needs to wait for each slave node
to request the mapping, and then may need to reserialize and compress the
object data. We test the time to commit and sync the data using different
compression engines.
